---
title: "result2"
author: "Takuto Yoshida"
date: "2022-12-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
# Make the following libraries available
library('readr') 
library('dplyr') 
library('ggplot2') 
library('gridExtra')
library('caret') 
library('randomForest')
library('glmnet')
library('kernlab')
library('tidyverse')
library('stringr')
library('corrplot')
library('scales')
library('ggthemes')
```

```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
# Importing the dataset
theme_set(theme_light())
setwd("/Users/yoshidatakuto/Dropbox/HSPH/MPH-CLE/BST260/titanic (1)")
train_titanic <- read.csv("test.csv", stringsAsFactors = F) %>% mutate(Test_Data = 0)
test_titanic <- read.csv("train.csv", stringsAsFactors = F) %>% mutate(Test_Data = 1)
titanic_full <- bind_rows(train_titanic, test_titanic) 
```

# **3. Feature Engineering $ Missing Value Imputation**
## **3.1 Feature Engineering**
### **3.1.1 Title**
From the evaluation of the variables so far, I have found that survival rates are higher for economically well-off individuals and for women. Thus, it is possible that survival rates can be predicted from name titles. I subtracted the Title from *Name* by using regular expression.
```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
titanic_full$Title <- gsub('(.*, )|(\\..*)', '', titanic_full$Name)
titanic_full$Surname <- sapply(titanic_full$Name, function(x) strsplit(x, split = '[,.]')[[1]][1])
table(titanic_full$Title, titanic_full$Survived)
table(titanic_full$Sex, titanic_full$Title)
prop.table(table(titanic_full$Title, titanic_full$Survived), 1)
```

```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
ggplot(titanic_full[1:891, ], aes(x = Title, fill = factor(Survived))) + 
  geom_bar(stat='count', position='dodge') 
```
There are several few titles. We have summarized and categorized them into groups of six titles.

```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
officer <- c('Capt', 'Col', 'Don', 'Dr', 'Major', 'Rev')
royalty <- c('Dona', 'Lady', 'the Countess', 'Sir', 'Jonkheer')
titanic_full$Title[titanic_full$Title == 'Mlle'] <- 'Miss'
titanic_full$Title[titanic_full$Title == 'Ms'] <- 'Miss'
titanic_full$Title[titanic_full$Title == 'Mme'] <- 'Mrs'
titanic_full$Title[titanic_full$Title %in% royalty] <- 'Royalty'
titanic_full$Title[titanic_full$Title %in% officer] <- 'Officer'
titanic_full$Title = as.factor(titanic_full$Title)
```

```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
ggplot(titanic_full[1:891,],aes(x=Title, fill=factor(Survived))) +
  geom_bar(stat='count', position='dodge') 
```
It can be seen that the mortality rate is very high for those with the title "Mr.".

### **3.1.2 Cabin data**
Many part of cabin data was missing. Since assigning missing values would place a very strong presumption, I made it a binary variable with and without data.

```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
titanic_full$Cabin_dat <- ifelse(!(titanic_full$Cabin==""), 1, 0)
prop.table(table(titanic_full$Cabin_dat))
```

### **3.1.3 Fare (per person)**
We created the per capita fare cost as a variable because it is possible that more affluent people purchase more expensive tickets and have higher survival rates.
```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
fare_pp <- titanic_full %>%
  group_by(Ticket, Fare) %>%
  summarise(Group_size_FE = n()) %>%
  mutate(Fare_pp_FE = Fare / Group_size_FE)
```
```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
titanic_full <- left_join(titanic_full, fare_pp, by=c("Ticket", "Fare"))
```

```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
g13 <- ggplot(titanic_full, aes(x = Group_size_FE, y = Fare)) + 
  geom_jitter(alpha = 0.2) + 
  geom_smooth(method = "lm", se = F) + 
  scale_y_continuous(limits = c(0, 300)) + 
  labs(x = "Group Size", y = "Fare") + 
  theme(legend.position = "none")

g14 <- ggplot(titanic_full, aes(x = Group_size_FE, y = Fare, col = factor(Pclass))) + 
  geom_jitter(alpha = 0.2) + 
  geom_smooth(method = "lm", se = F) + 
  facet_grid(Pclass ~ ., labeller = label_both) + 
  scale_y_continuous(limits = c(0, 300)) + 
  labs(x = "Group Size", y = "Fare") + 
  theme(legend.position = "none")

grid.arrange(g13, g14, ncol = 2)
```
There are correlation between Group size and Pclass.
### **3.1.4**
Based on previous studies, it is possible that the larger the family size, the higher the survival rate. Thus, I created a family size variable.
```{r, appendix = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
titanic_full$Family_size_FE <- titanic_full$SibSp + titanic_full$Parch + 1

titanic_full$Total_group_size_FE <- pmax(titanic_full$Family_size_FE, titanic_full$Group_size_FE)
```
